---
title: "Alcohol vs Seat choice"
author: "Rita Jarbanda"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.
$H_A$: The average number drinks is different between at least two rows. 




#method

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

We have changed all the character variables to factor variables.The type of this problem needs a numerical variable called Alcohol and a factor variable called Seat We will be using different helper files to help us complete the analysis of Numerical and factorial variables.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The fancy notch displays the three categories of seating arrangements which was the front, middle and back. We can observe that people who are seated in the back had a median that differed while the people in the front and back had more confident median plot.
We can assume that people in the back consume more alcoholic drinks compared to those who were seated in the middle and front rows.


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
``` 

The numerical data shows that the average number of drinks for the people seated in the back is about 9 drinks.
This is three times the average number of drinks for those who are seated in the middle. 
This is also nine times average number of drinks for those who are seated in the front.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The one way anova inferential test  shows a small p-value which is 0.000116, which means that there is a probability of having no difference between alcohol consumed between the front, middle and back rows that are available for people to be seated in.

```{r}
plot(TukeyHSD(model1))
```

## Conclusions


